Creating an Evolution Simulator for Protein Low Complexity Regions and Attempting to Utilize it for an Approximate Bayesian Computation

### 2023-03-29 beap_pres_dec2022/beap_pres_dec.tex
presentation updates

% Title page details: 
\title[BEAP Dec 2022]{Estimating Evolutionary Parameters for Protein Low Complexity Regions using an Approximate Bayesian Computation} 
\author{Alexander Turco}
\date{December 5, 2022}
\logo{\includegraphics[height=1cm, width=1cm]{logo.png}}

@@

		  		\begin{block}{} \hyperlink{link1}{Background Information} \end{block}
		  		\begin{block}{} Research Questions/Explorations \end{block}
		  		\begin{block}{} Experimental Approach \end{block}
		  		\begin{block}{} Future Work \end{block}

@@

	%For my Research questions/Exploration slides, I will talk about things such as
	%SLIDE 9%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\section{Research Questions/Exploration}

	\begin{frame}{What Did we Do in this Study?}
		\begin{itemize}
			\item Programmed an ABC-MCMC using \texttt{C++} which consisted of a simulation step where amino acid sequences were altered by point mutations and insertions/deletions \newline
			\item Utilized the exponential distribution with ($\beta$ = length*indel\_rate) to examine if the length of a repeat plays a role in its mutation \newline
			\item Attempted to estimate evolutionary parameters such as mutation rates and insertion/deletion rates \newline
			\item Explored summary statistics that could quantitatively explain characteristics of LCRs

@@

	%For my Experimental approach slides, I will talk about things such as 
	%SLIDE 10%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\section{Experimental Approach}
	\begin{frame}{What Approach will be Taken?}

@@

	%Slide 14 - Maybe to this slide - Maybe throw in extra slides for reference
	\begin{frame}{Simulation Step}
		\begin{center}
			\begin{enumerate}
			\item Random Protein Sequence \newline	
			GGAGGGAQ \newline		
			mutation rate = 0.14
			\qquad exp($\beta$), where $\beta$ = mutation rate\newline 
			indel rate = 0.14 \qquad exp($\beta$), where $\beta$ = length of repeat * indel rate \newline \pause

			\item Assign Exponential Deviates \newline
			mutation deviates = (0.83, 1.82, 2.35, 0.54, 0.98, 0.76, 1.53, 2.34) \newline
			indel deviates = (0.21, 1.21, 1.49, 0.86, 0.97, 1.13, 0.53, 0.35) \newline \pause

			\end{enumerate}
		\end{center}

	%For my Results slides, I will talk about things such as the results I have, But i don't have any right now
	%SLIDE 15%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\section{Results}
	\begin{frame}{Results}

>>>>

% Title page details: 
\title[BEAP Dec 2022]{Creating an Evolution Simulator for Protein Low Complexity Regions and Attempting to Utilize it for an Approximate Bayesian Computation} 
\author{Alexander Turco}
\date{December 5, 2022}
\logo{\includegraphics[height=1cm, width=1cm]{logo.png}}

@@

		  		\begin{block}{} \hyperlink{link1}{Background Information} \end{block}
		  		\begin{block}{} Simulating LCR Evolution \end{block}
		  		\begin{block}{} Applications to ABC-MCMC \end{block}
		  		\begin{block}{} Conclusions \end{block}
		  		\begin{block}{} Future Work \end{block}

@@

	\begin{frame}{What we Did in this Study}
		\begin{itemize}
			\item 
		\end{itemize}
	\end{frame}

	%For my Research questions/Exploration slides, I will talk about things such as
	%SLIDE 9%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\section{Simulating LCR Evolution}

	\begin{frame}{LCR Simulator Overall Process}
		\begin{center}
			\begin{enumerate}
				\item Random Protein Sequence \newline	
				GGAGGGAQ \newline		
				mutation rate = 0.14
				indel rate = 0.14  \newline\pause

				\item Assign Exponential Deviates \newline
				mutation deviates = (0.83, 1.82, 2.35, 0.54, 0.98, 0.76, 1.53, 2.34) \newline
				indel deviates = (0.21, 1.21, 1.49, 0.86, 0.97, 1.13, 0.53, 0.35) \newline
				\qquad exp($\beta$), where $\beta$ = mutation rate\newline 
				\qquad exp($\beta$), where $\beta$ = length of repeat * indel rate \newline \pause

			\end{enumerate}
		\end{center}	
	\end{frame}

	\begin{frame}{LCR Simulator Results}

@@

	\begin{frame}{LCR Simulator Results 2}

	\begin{frame}{LCR Simulator Results 3}

	\begin{frame}{LCR Simulator Results 4}

	%Say something like, before we get into how this simulation can be used in an approximate bayesian computation, were just going to go through a very simple overview of bayesian statistics
	\section{Applications to ABC-MCMC}
	\begin{frame}{Bayesian Statistics Overview}

@@

	%Slide 14 - Maybe to this slide - Maybe throw in extra slides for reference
